Changes to police demand in COVID-19 pandemic

### 2022-03-13 docs/index.Rmd
adding slides as the gh pages

all_calls <- read_rds("/Volumes/n8_covid/all_calls_forecast.Rds")
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
attended_by_grade_forecast <- read_rds("/Volumes/n8_covid/attended_by_grade_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")
by_grade_tos_forecasts <- read_rds("/Volumes/n8_covid/by_grade_tos_forecasts.Rds")
cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "2020"))
total_calls_by_imd <- read_csv("/Volumes/n8_covid/total_calls_by_imd.csv")
weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")

>>>>

all_calls <- read_rds("/Volumes/n8_covid/all_calls_forecast.Rds")
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
attended_by_grade_forecast <- read_rds("/Volumes/n8_covid/attended_by_grade_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")
by_grade_tos_forecasts <- read_rds("/Volumes/n8_covid/by_grade_tos_forecasts.Rds")
cheshire_lsoas <- st_read("../cheshire_lsoas.geojson")
lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "2020"))
total_calls_by_imd <- read_csv("/Volumes/n8_covid/total_calls_by_imd.csv")
weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
